Analysis of split plot design using MCMCglmm

### 2018-04-06 README.Rmd
Update Travis badge link

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Travis-CI Build Status](https://travis-ci.org/phytopathology/rice_awd_pests.svg?branch=master)](https://travis-ci.org/phytopathology/rice_awd_pests)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/phytopathology/rice_awd_pests?branch=master&svg=true)](https://ci.appveyor.com/project/phytopathology/rice_awd_pests)

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/rice_awd_pests.svg?branch=master)](https://travis-ci.org/openplantpathology/rice_awd_pests)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/phytopathology/rice_awd_pests?branch=master&svg=true)](https://ci.appveyor.com/project/phytopathology/rice_awd_pests)
